Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-13 paper/structureScene.tex
Swap figures 3 and 4

This section presents evaluation results for the ASSR settings. The $p@k$ for different settings are shown in Figures \ref{fig:ASS_1} and \ref{fig:ASS_2}, illustrating the effect of the different similarity metrics and the influence of the logarithm, respectively.

>>>>

This section presents evaluation results for the ASSR settings. The $p@k$ for different settings are shown in Figures \ref{fig:ASS_2} and \ref{fig:ASS_1}, illustrating the effect of the different similarity metrics and the influence of the logarithm, respectively.
